%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Founder} % Job title
    {Algorithmic Trading Team} % Organization
    {Saudi Arabia} % Location
    {Jan. 2017 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {To be a founder of algorithmic trading team, I am mainly working on designing crypto trading system and algorithms, e.g., API to access account in multiple crypto exchanges, smart AI system to capture hourly speculation opportunities, real-time parallel analyzing market, etc. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern Developer} % Job title
    {Sadeem (Startup Company in Saudi Arabia)} % Organization
    {Saudi Arabia} % Location
    {Mar. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hardware: designed C++ driver and API for sonic, camera, infrared light sensors on a hardware motherboard, deployed first generation system.}
        \item {Code Refactoring: re-designed software architecture for sensor data communication, vehicle detection and emergency event detection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {HKUST Robotics Institute} % Organization
    {Hong Kong, China} % Location
    {Jan. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {To be a research assistant in RI, HKUST, I designed vision (image processing, tracking, segmentation) algorithm for UAV and home robot.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {DJI} % Organization
    {ShenZhen, China} % Location
    {Sep. 2014 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed robust visual tracking algorithm for Phantom 4 UAV in long term tracking situation and complex environment.}
        \item {Supported product-level design for deploying algorithms to low cost UAV system and design the I/O interface for GPS and sensor.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {State Key Laboratory of Integrated Services Networks} % Organization
    {China} % Location
    {Jun. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed Ad-hoc network for vehicle navigation and surveillance by sensor and GPS.}
        \item {Developed software interface to solve real-time data visualization and processing (C++).}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
